%-------------------------------------------------------------------------------
%  SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%  CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  \cventry
    {Senior Data Engineer} % Job title
    {Tata Consultancy Services (TCS)} % Organization
    {Aylesbury, UK} % Location
    {Jan. 2024 -- Present} % Date(s)
    {
      \begin{cvitems}
        \item {Acted as the primary interface between business stakeholders and technical delivery teams, owning requirements gathering, solution design, process improvement, and operational reporting for a major enterprise client.}
        \item {Built Python-based automation systems that improved operational data processing and reduced turnaround time across engineering teams.}
        \item {Fine-tuned GPT models on custom CSV datasets to improve accuracy for domain-specific text classification.}
        \item {Collaborated with cross-functional groups including operations, planning, and management to translate requirements into scalable data solutions.}
        \item {Identified a recurring operational bottleneck and proposed an automated Python-based solution (Quick Win tool); partnered with engineering teams to deliver and roll out the tool, now used daily across the business.}
        \item {Conducted root cause analysis on data quality issues, mapped impacted processes, and coordinated cross-functional delivery of fixes including automated detection and reporting tools.}
        \item {Ensured data integrity through structured RCA, impact assessments, and continuous process improvement.}
        \item {Built and maintained Power BI dashboards and management information reports for senior stakeholders, enabling data-driven visibility of KPIs and project status.}
        \item {Facilitated workshops and working sessions with clients and delivery teams to review requirements, assess change impact, and align priorities.}
      \end{cvitems}
    }

  %---------------------------------------------------------
  \cventry
    {Business Analyst} % Job title
    {Tata Consultancy Services (TCS)} % Organization
    {Hyderabad, India (Supporting UK Operations)} % Location
    {Jul. 2019 -- Dec. 2023} % Date(s)
    {
      \begin{cvitems}
        \item {Provided business analysis and data support to UK-based planning and operations teams on a large-scale national infrastructure programme.}
        \item {Engaged directly with UK client stakeholders to capture and document business requirements, agree process changes, and translate them into functional specifications.}
        \item {Identified a gap in an operational process and implemented a new approach that enabled the business to serve previously missed customers, contributing to programme targets.}
        \item {Mapped and analysed end-to-end business processes to identify inefficiencies, support SLA management, and drive continuous improvement.}
        \item {Developed SQL queries, stored procedures, and PL/SQL packages to automate data extraction, reporting, and order lifecycle tracking.}
        \item {Produced management information packs and ad hoc analysis for leadership, providing programme-level insights for decision-making.}
        \item {Coordinated task progression across multiple teams, managing dependencies and resolving issues to keep order lifecycles on track within SLAs.}
        \item {Participated in client review meetings to define process requirements, capture change requests, and communicate progress.}
      \end{cvitems}
    }

  %---------------------------------------------------------
\end{cventries}
